\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}

% Define colors
\definecolor{darkblue}{RGB}{0, 51, 102}
\definecolor{lightgray}{RGB}{240, 240, 240}

% Set up the page margins
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

% Set up the color of sections and subsections
\colorlet{heading}{darkblue}
\colorlet{accent}{darkblue}
\colorlet{emphasis}{black}
\colorlet{body}{black!80!white}

% Adjust font sizes
\renewcommand{\namefont}{\Huge\bfseries}
\renewcommand{\personalinfofont}{\large}
\renewcommand{\cvsectionfont}{\Large\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}
\newcommand{\cveventfont}{} % Define if not already defined
\newcommand{\cveventfont}{} % Define if not already defined
\renewcommand{\cveventfont}{\normalsize\bfseries}

% Personal information
\name{OUAHID OMAR}
\tagline{AI-Focused Data Engineer}
\personalinfo{%
  \email{omarouahid.98@gmail.com}
  \phone{+212680364513}
  \linkedin{omar-ouahid}
  \location{Casablanca, Morocco}
  
}

\begin{document}
\makecvheader % This command prints the CV header

\cvsection{Professional Summary}
\begin{minipage}{\textwidth}
Experienced AI-focused Data Engineer with proven expertise in designing and implementing scalable data pipelines, machine learning infrastructure, and AI-powered data processing systems. Skilled in architecting end-to-end data solutions that support ML/AI workflows using modern cloud platforms and orchestration tools. Demonstrated ability to transform raw data into valuable business insights through robust ETL/ELT processes, feature engineering, and automated ML pipelines. Strong background in optimizing data systems for AI/ML workloads, performance, and scalability.
\end{minipage}

\cvsection{Professional Experience}
\cvevent{Data Engineer at DXC Technology}{May 2024 - Present}{}{Casablanca, Morocco}
\begin{itemize}[noitemsep]
\item Architected and implemented scalable data pipeline systems using AWS services (Fargate, ECR, Step Functions) with automated CI/CD deployment processes.
\item Designed and built ETL pipelines for healthcare laboratory data processing, handling multiple data formats and ensuring data quality and consistency.
\item Developed API-driven data ingestion systems that dynamically generate data workflows from OpenAPI specifications, enabling flexible data source integration.
\item Implemented real-time data processing solutions using AWS Lambda and Step Functions for complex workflow orchestration and monitoring.
\item Built and maintained data preparation workflows optimized for downstream analytics and machine learning applications.
\item Established data governance and quality assurance processes, ensuring reliable data delivery across multiple business units.
\end{itemize}

\cvevent{Data Engineer at Berexia (External at SCOR)}{Sep 2021 - Jan 2024}{}{Casablanca, Morocco}
\begin{itemize}[noitemsep]
    \item Designed and implemented automated data extraction and transformation pipelines using Python, reducing manual processing time by 70\%.
    \item Built scalable ETL systems for insurance data processing, handling millions of records with high availability and fault tolerance.
    \item Developed data validation and quality monitoring frameworks to ensure data integrity across multiple source systems.
    \item Created RESTful APIs and microservices architecture using Flask for efficient data access and integration.
    \item Implemented real-time data visualization dashboards using Dash, enabling stakeholders to monitor key business metrics.
    \item Optimized database performance and designed data models for improved query efficiency and storage optimization.
\end{itemize}

\cvevent{Data Scientist at Adwebmaroc}{Mar 2021 - Aug 2021}{}{Casablanca, Morocco}
\begin{itemize}[noitemsep]
    \item Developed an automated brand detection system with Python, OpenCV, TensorFlow, and YOLOv5.
    \item Used advanced image processing for brand element detection.
    \item Implemented OCR to enhance data richness and accuracy.
    \item Applied NLP for comprehensive analysis of extracted text.
    \item Enhanced system efficiency with a custom-tuned YOLOv5 model.
    \item Combined computer vision, OCR, and NLP for robust brand detection.
\end{itemize>

\newpage
\cvsection{Education}
\cvevent{Master's Degree in Engineering (Diplôme d'Ingénieur) - Data Science and Computer Science Engineering}{Institut National des Postes et Télécommunications}{2018 - 2021}{}
\cvevent{Intensive preparatory coursework in scientific disciplines}{CPGE - Classes Préparatoires aux Grandes Écoles}{2016 - 2018}{}


\cvsection{Projects}

\cvevent{Real-time Customer Data Pipeline}{}{2024}{}
\begin{itemize}[noitemsep]
    \item Architected and implemented a comprehensive data pipeline solution for Catawiki's customer support system, processing real-time user interaction data.
    \item Built scalable data ingestion and transformation pipelines using Python and cloud-native services to handle high-volume customer data streams.
    \item Implemented vector database solutions (ChromaDB) for efficient storage and retrieval of customer interaction patterns and support documentation.
    \item Designed automated data quality monitoring and validation systems to ensure data integrity across the entire pipeline.
    \item Created RESTful API endpoints using Flask for real-time data access and integration with downstream applications.
    \item Established monitoring and alerting systems for pipeline performance optimization and proactive issue resolution.
\end{itemize}


\cvsection{Skills}

\textbf{Programming Languages}
\begin{itemize}
  \item Proficient: Python, SQL
  \item Familiar: Java, Scala, R
\end{itemize}

\textbf{Data Engineering Platforms \& Tools}
\begin{itemize}
  \item Big Data Processing: Apache Spark, Hadoop ecosystem
  \item Workflow Orchestration: Apache Airflow, AWS Step Functions
  \item Data Storage: PostgreSQL, MySQL, MongoDB, Redis
  \item Message Queues: Apache Kafka, AWS SQS, RabbitMQ
  \item Data Warehousing: Amazon Redshift, Google BigQuery, Snowflake
  \item Vector Databases: Pinecone, ChromaDB, Weaviate
\end{itemize}

\textbf{Cloud Computing \& Infrastructure}
\begin{itemize}
  \item AWS Services: Lambda, EC2, Fargate, Step Functions, CloudWatch, S3, RDS, Redshift, Glue, Kinesis
  \item Containerization: Docker, Kubernetes
  \item Infrastructure as Code: Terraform, CloudFormation
  \item CI/CD Pipelines: Jenkins, GitLab CI, AWS CodePipeline
\end{itemize}

\textbf{AI/ML Data Engineering}
\begin{itemize}
  \item ML Pipeline Development: TensorFlow, PyTorch, scikit-learn, MLflow
  \item Feature Engineering: Advanced feature stores and ML data preparation
  \item Model Serving: Real-time and batch inference pipelines
  \item MLOps: Model versioning, monitoring, and automated retraining pipelines
  \item LLM Infrastructure: RAG systems, vector databases, prompt engineering workflows
\end{itemize}

\textbf{ETL/ELT \& Data Processing}
\begin{itemize}
  \item Data Manipulation: Pandas, NumPy, Dask
  \item Stream Processing: Apache Kafka, AWS Kinesis
  \item Batch Processing: Apache Spark, AWS Glue
  \item Data Quality: Great Expectations, custom validation frameworks
\end{itemize}

\textbf{API Development \& Integration}
\begin{itemize}
  \item RESTful APIs: Flask, Django, FastAPI
  \item Microservices Architecture: Design and implementation of scalable distributed systems
  \item API Gateway: AWS API Gateway, Kong
\end{itemize}

\textbf{Data Visualization \& Monitoring}
\begin{itemize}
  \item Dashboards: Plotly, Dash, Grafana
  \item Monitoring: CloudWatch, Prometheus, DataDog
  \item Business Intelligence: Tableau, Power BI
\end{itemize}

\textbf{Version Control \& Collaboration}
\begin{itemize}
  \item Git, GitHub, GitLab
  \item Agile methodologies and DevOps practices
\end{itemize}



\cvsection{Licenses \& Certifications}
\begin{itemize}[noitemsep]
    \item AWS Certified Solutions Architect (In Progress)
    \item Amazon SageMaker - LinkedIn
    \item Google Cloud Platform Data Engineering (In Progress)
\end{itemize}



\end{document}